\section{Detector Level Object Selection}
\label{sec:ObjReconstruction}

This section summarizes the detector-level selections applied to the three physics objects, electrons, muons, and jets used in the measurement. Each physics object of the analysis has two categories: \textit{baseline} and \textit{signal}. Physics objects satisfying a set of kinematic selections or looser identification criteria are categorized as \textit{baseline}. In contrast, the baseline objects that pass either stricter kinematic selections or additional isolation and track-to-vertex association (TTVA) requirements are categorized as \textit{signal objects}.

\subsection{Electrons}
\label{subsec:ElecRecon}

As discussed in Section \ref{subsec:ParticleRecon_Elec}, electrons are reconstructed by matching the inner detector track to an energy cluster in the electromagnetic calorimeter. Baseline electron objects are required to satisfy the kinematic selections of $\Pt~ > 7$ GeV $ \&~ |\eta| < 2.47$ and a loose likelihood identification working point of \textit{LHVeryLoose}. To avoid the wrongfully identified electrons reconstructed from pile-up tracks matched to the calorimeter cluster, a loose vertex association requirement of $|z_{0}\sin\theta| < 0.5 $ mm is applied to the baseline electron candidates.

Signal electrons are required to pass a more stringent loose likelihood identification, \textit{LHLooseBL}, which requires at least one hit in the innermost layer of the pixel detector (IBL). The signal electrons are distinguished by requiring the impact parameter significance of the baseline electrons to be $d_{0}/ \dZeroSig < 5$ and an isolation working point identification of \textit{LooseVarRad}. Table \ref{tab:Electron_RecoSel} summarizes the several selections imposed to define the baseline and signal electrons.

\begin{table}[ht]
    \centering
        \caption{Definition of the baseline and signal electrons.\label{tab:Electron_RecoSel}}
        \begin{tabular}{|| l || c | c ||}
        \hline
        Selection Category & \textbf{Baseline} & \textbf{Signal} \\
        \hline\hline
        Kinematic cuts & $p_{T}~ > 7$ GeV & $ p_{T}~ > 7$ GeV \\
                    & $|\eta| < 2.47$  &  $|\eta| < 2.47$\\
        \hline  
        Identification & LHVeryLoose & LHLooseBL \\
        \hline 
        Vertex Association & $|z_{0}\sin\theta| < 0.5$ mm & $|z_{0}\sin\theta|< 0.5$ mm\\
        \hline
        Isolation Working Point & $-$ & LooseVarRad\\
        \hline 
        Impact Parameter Significance & $-$ & $d_{0}/ \sigma_{d_{0}} < 5$ \\
        \hline
    \end{tabular}
\end{table}

\subsection{Muons}
\label{subsec:MuonRecon}
As discussed in Section \ref{subsec:ParticleRecon_Muon}, different types of muons are reconstructed utilizing information from the inner detector, the muon spectrometer, and the calorimeters. All baseline muons are required to satisfy $ |\eta| < 2.7 $, $p_{T} > 5$ GeV, a loose impact parameter requirements of $|z_{0}\sin\theta| < 0.5 $ mm, and \textit{Loose} identification working point. The signal muons are identified from the baseline muons by requiring additional isolation identification of \textit{PflowLooseVarRad} and TTVA requirements of $d_{0}/\sigma_{d_{0}} < 3$. Table \ref{tab:muon_baseline_signal} summarizes baseline and signal muons selection requirements.

\begin{table}[ht]
    \centering
        \caption{Definition of the baseline and signal muons.\label{tab:muon_baseline_signal}}
        \begin{tabular}{|| l || c | c ||}
        \hline
        Selection Category & \textbf{Baseline} & \textbf{Signal} \\
        \hline\hline
        Kinematic cuts & $p_{T}~ > 5$ GeV & $p_{T}~ > 5$ GeV \\
                    & Calo-tagged $ p_{T}~ > 15$ GeV & Calo-tagged $ p_{T}~ > 15$ GeV \\
              & $|\eta| < 2.7$ & $|\eta| < 2.7$\\
        \hline
        Identification & Loose & Loose \\
        \hline 
        Vertex Association & $|z_{0}\sin\theta| < 0.5$ mm & $|z_{0}\sin\theta|< 0.5$ mm\\
        \hline
        Isolation Working Point & $-$ & PflowLooseVarRad\\
        \hline 
        Impact Parameter Significance & $-$ & $d_{0}/\sigma_{d_{0}} < 3$ \\
        \hline
    \end{tabular}
\end{table}

\subsection{Jets}
\label{subsec:JetRecon}
Jets are reconstructed with the particle flow anti$-K_{T}$ clustering algorithm using a radius parameter of $R = 0.4$ as discussed in Section \ref{subsec:ParticleRecon_Jets}. The reconstructed jets that meet $p_{T}~ > 15$ GeV and $ |\eta| < 4.5 $ kinematic requirements are classified as baseline jets. Baseline jets in $ |\eta| < 2.4 $ satisfying the \textit{Tight} working point of the \textit{Jet-vertex-tagger (JVT)} tool, and in $ |\eta| > 2.5 $ satisfying the \textit{Tight} working point of \textit{forward-jet-vertex-tagger (fJVT)} tool are classified as signal jets. Table \ref{tab:jets} summarizes the details of baseline and signal jets selection. 

A particular type of jets \textit{b-jets}, containing b-hadrons initiated from a b-quark, are also used for the background estimation. The b-jets reconstruction relies on multivariate analysis (MVA), utilizing the fact that b-hadrons have a long mean lifetime of order picoseconds, leading to a displaced secondary vertex in the detectors. A tagger discussed in detail in Ref \cite{bTagging} with b-tagging efficiency of $77\%$ is used in the analysis to identify the b-jets.

\begin{table}[ht]
    \centering
    \caption{Definition of the baseline and signal jets.\label{tab:jets}}
        \begin{tabular}{|| l || c | c ||}
        \hline
        Selection Category & \textbf{Baseline} & \textbf{Signal} \\
        \hline\hline
        Kinematic cuts & $\Pt~ > 30$ GeV & $\Pt~ > 30$ GeV \\
             & $|\eta| < 4.5$ & $|\eta| < 4.5$\\
        \hline 
        Identification & AntiKt4EMPFlow & AntiKt4EMPFlow\\
        \hline
        Jet-Vertex-Tagger & $-$ & $ |\eta| < 2.4 $ JVT ("Tight")\\
                & $-$ & $|\eta| > 2.5 $ fJVT ("Tight")\\
        \hline
    \end{tabular}
\end{table}

\subsection{Overlap Removal}
\label{subsec:OR}

In order to avoid double-counting detector signals in the reconstruction of physics objects, an \textit{overlap removal} procedure is applied to remove the physics objects reconstructed from the same detector signal. The measurement uses a lepton-favored overlap removal which selects leptons over jets. Overlap removal is an iterative process in which only objects surviving all previous steps are used in the subsequent steps. Table \ref{tab:overlap_removal} summarizes the overlap removal steps, where the $\Delta R$ is the angular separation between objects calculated using rapidity.

\begin{table}[ht]
    \centering
        \caption{Overlap removal used in the analysis. An object removed in one step does not enter into the subsequent step. \label{tab:overlap_removal}}
        \begin{tabular}{|| l || c | c ||}
        \hline
        Remove Object & Accept Object & Overlap Criteria \\
        \hline\hline
        Electron & Electron & Share a track or have overlapping calorimeter cluster.\\
                &       & Keep electron with higher $p_{T}~$\\
        \hline
        Muon & Electron & Share ID track, and the muon is calo-tagged\\
        \hline
        Electron & Muon & Share ID track\\
        \hline
        Jet & Electron & $\Delta R_{e-jet} < 0.2$ \\
        \hline 
        Jet & Muon & $\Delta R_{\mu-jet} < 0.2/$ghost-associated and $N_{jet~tracks} < 3$\\
        \hline
    \end{tabular}
\end{table}