\part{\LARGE{Introduction}}
\label{sec:Introduction}
Particle Physics investigates the fundamental nature of the universe. The Standard Model (SM), the fundamental theory of Particle Physics, provides a theoretical formulation that explains all known elementary particles, their interactions, and three of the four fundamental forces observed in nature: strong, electromagnetic, and weak forces. Fifty years after its formulation, the parameters predicted by the SM have been measured experimentally with high precision. The experimental discovery of the Higgs boson in 2012 established the SM as a complete and highly successful theory. However, the lack of description of the fourth fundamental force, gravity, and other experimentally evident phenomena, such as the existence of dark matter, suggest that the SM provides only an incomplete description of nature. Still, experimental evidence of new physics Beyond the Standard Model (BSM) has yet to be observed. The current primary objective of the Large Hadron Collider (LHC) at CERN is to look for experimental evidence of new physics which might explain or resolve some of the shortcomings of the SM. 

New physics searches can be broadly categorized into two types, direct and indirect. The direct search focuses on finding experimental evidence of new physics signatures, such as new particles. In contrast, the indirect approach focuses on precisely measuring the parameters of the SM-predicted processes, looking for deviations compared to the state-of-the-art theoretical predictions. One critical phenomenon of the SM is the vector boson scattering (VBS) in final states involving vector bosons, which are force-mediating particles for the electroweak (EWK) force. VBS processes are mediated by the rare triple and quartic self-couplings between the vector bosons, whose SM amplitudes interfere destructively with the Higgs-mediated processes. Several BSM theories modify either the strength of the vector boson self-couplings or that of the Higgs-mediated processes, thus, altering the extent of the interference and, consequently, the cross-sections from the predicted values. As many new physics particles are expected to exist at high energies, such deviations are expected to appear at higher energies that have not been probed experimentally yet. 

This thesis presents an indirect approach to new physics searches in one of the VBS-sensitive multiboson final states. The measurement analyzes the data collected by the ATLAS experiment at the LHC from 2015-2018 to measure the VBS-sensitive production of two $Z$ bosons in association with two jets, where each $Z$ boson decays into a pair of same-flavor opposite-charge (SF-OC) leptons. The quartic self-coupling of the vector bosons in $ZZ^*(\rightarrow 4\ell)jj$ final state is experimentally accessible with the collected LHC dataset for the first time. The measurement uses a model-independent approach to look for anomalous quartic gauge couplings. Thus, measurements presented in this thesis are at the frontier of particle physics, pushing the boundaries of new physics searches through an indirect approach. 

The theory of SM, its shortcomings, and the $ZZ^*(\rightarrow 4\ell)jj$ process are discussed in Chapter $II$. The LHC and ATLAS experiments are then introduced in Chapter $III$. Chapters $IV$ and $V$ discuss the details of the measurement. The final results are presented in Chapter $VI$. 
